Modalities for Location Virtualization

### 2022-09-19 programlogic.tex

We present three main points-to relations as part of utilization of separation logic \ref{} as an ambient logic:
\begin{enumerate}
\item Physical address points-to, $\pfpointsto\locsf\locsf\ppts\qfrac$
\item Register points-to, $\pfpointsto\rg\rv\rpts\qfrac$
\item Virtual memory address points-to, $\pfpointsto\vaddr\locsf\vpts\qfrac$
\end{enumerate}
\paragraph{Register points-to} The assertion $\pfpointsto\rg\rv\rpts\qfrac$ ensures the ownership of the register $\rg$ naming the register value $\rv$. The fraction $\qfrac$ with value 1 asserts the unique ownership of the register mapping, and grants update permission on it, otherwise, any value $0 < \qfrac <1$ represents partial ownership granting readonly permission on the mapping.
\paragraph{Physical-Memory points-to} The our physical memory points-to relation ($\pfpointsto\locsf\locsf\ppts\qfrac$) exhibits nested-mappings due to masking applied on the indexing address ($\locsf$). The unfolded definition of the physical mapsto 
\[
\begin{array}{cl}
\pfpointsto\locsf\locsf\ppts\qfrac \stackrel{def}{=} & \nfpointsto{\mask\locsf\tw}{\mask\locsf\ft}\locsf\qfrac\naddr
\end{array}
\]
where we simply abstract the generation of hierarchical mapping of a physical address ($\locsf$) through the different masks of the address ($\locsf|^{12}$ and $\locsf|^{52}$) as nested map resources.
\paragraph{Virtual-Memory points-to} As we see in Figure \fref{fig:}, virtual address mapping is obtained via traversal of page table, i.e. indirection provided by physical memory lookups. As expected, we define the virtual-points to relation, ($\pfpointsto\vaddr\locsf\vpts\qfrac$), in terms of multiple physical memory mappings representing the indirection shown in Figure \fref{fig:}
\[
\begin{array}{cl}
\pfpointsto\locsf\locsf\ppts\qfrac \stackrel{def}{=} & \nfpointsto{\mask\locsf\tw}{\mask\locsf\ft}\locsf\qfrac\naddr
\end{array}
\]
\subsection{Modal Abstraction for Virtualizing Memory Locations}
\label{sec:credits}
\input{fig-laws}

\subsection{Memory Deallocation as a Ghost Operation}
\label{sec:free}

>>>>

We present three main points-to relations as part of utilization of separation logic \ref{} as an ambient logic:
\begin{enumerate}
\item Physical address points-to, $\pfpointsto\locsf\locsf\ppts\qfrac$
\item Register points-to, $\pfpointsto\rg\rv\rpts\qfrac$
\item Virtual memory address points-to, $\pfpointsto\vaddr\locsf\vpts\qfrac$
\end{enumerate}
\paragraph{Register points-to} The assertion $\pfpointsto\rg\rv\rpts\qfrac$ ensures the ownership of the register $\rg$ naming the register value $\rv$. The fraction $\qfrac$ with value 1 asserts the unique ownership of the register mapping, and grants update permission on it, otherwise, any value $0 < \qfrac <1$ represents partial ownership granting readonly permission on the mapping.
\paragraph{Physical-Memory points-to} The our physical memory points-to relation ($\pfpointsto\locsf\locsf\ppts\qfrac$) exhibits nested-mappings due to masking applied on the indexing address ($\locsf$). The unfolded definition of the physical mapsto 
\begin{figure}[!ht]
\[
\begin{array}{cl}
\pfpointsto\locsf\locsf\ppts\qfrac \stackrel{def}{=} & \nfpointsto{\mask\locsf\tw}{\mask\locsf\ft}\locsf\qfrac\naddr
\end{array}
\]
\caption{Physical Points-to with Nested Masking}
  \label{fig:physicalpointsto}
\end{figure}
where we simply abstract the generation of hierarchical mapping of a physical address ($\locsf$) through the different masks of the address ($\locsf|^{12}$ and $\locsf|^{52}$) as nested map resources.
\paragraph{Virtual-Memory points-to} As we see in Figure \fref{fig:}, virtual address mapping is obtained via traversal of page table, i.e. indirection provided by physical memory lookups. As expected, we define the virtual-points to relation, ($\pfpointsto\vaddr\locsf\vpts\qfrac$), in terms of multiple physical memory mappings representing the indirection shown in Figure \fref{fig:}
\begin{figure*}
\[
\begin{array}{cl}
  \pfpointsto\locsf\locsf\ppts\qfrac \stackrel{def}{=} \lambda \tlf\Loc.
  & \exists_{ \tlfoff\Locn \;, \tltoff\Locn \;, \tltwoff\Locn \;, \tlooff\Locn \;, \tpgoff\Loctw \;, \tlt\Loc \;, \tltw\Loc \;, \tlo\Loc \tpg\Loc   }
\end{array}
\]
\caption{Virtual Points-to Relation}
  \label{fig:virtualpointsto}
\end{figure*}

\begin{comment}
   Definition virt_mapsto (a:word 64) (v:word 64) (q:Qp) : word 64 -> iProp Σ :=
λ (cr:word 64) ,
     ( ⌜ aligned a ⌝ ∗
         ∃ (l3 l2 l1 page w :word 64) (pageoff:word 12) (l4off l3off l2off l1off:word 9) ,
           ⌜ (WordImpl.concat (wzero 16) (WordImpl.concat l4off (WordImpl.concat l3off (WordImpl.concat l2off (WordImpl.concat l1off pageoff))))) = a ⌝ ∗
                          (natToWord 64 ((wordToNat l4)+(8*(wordToNat l4off)))) ↦p{q} (l3  ^|  (natToWord 64 3)) ∗
                          (natToWord 64 ((wordToNat l3)+(8*(wordToNat l3off)))) ↦p{q} (l2  ^|  (natToWord 64 3)) ∗
                          (natToWord 64 ((wordToNat l2)+(8*(wordToNat l2off)))) ↦p{q} ( l1  ^|  (natToWord 64 3)) ∗
                          (natToWord 64 ((wordToNat l2)+(8*(wordToNat l1off)))) ↦p{q} ( page  ^|  (natToWord 64 3)) ∗
                          (natToWord 64 ((wordToNat page) +(wordToNat pageoff))) ↦p v )%I.
\end{comment}

\subsection{Modal Abstraction for Virtualizing Memory Locations}
\label{sec:modallocationvirtualization}
\input{fig-laws}
